Figures

### 2019-08-06 figures/07_model-selection.Rmd
towards a re results table
organize figs for ms

```{r tn_fe, out.width="3.25in", out.height="4in"}
# lapply(re_brms, function(x) x$formula) 
fit_tn         <- re_brms[[5]] # 5 is best tn model with random effects
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

```{r re-comparison}
# tp, tn
# ag, row_crop, pasture, corn, soybeans
re_global <- dplyr::rbind_all(lapply(re_brms, function(x) x$re_global))
re_global$term <- unlist(lapply(re_brms, 
                                function(x) get_re_text(as.character(x$formula)[1])))
re_global$response <- c(rep("tp", 5), rep("tn", 5))
re_global <- dplyr::filter(re_global, term != "rowvcropvpct")

# loo_compare(loo(re_brms[[1]]), loo(re_brms[[2]]), loo(re_brms[[3]]),
#             loo(re_brms[[4]]), loo(re_brms[[5]]))
# loo_compare(loo(re_brms[[6]]), loo(re_brms[[7]]), loo(re_brms[[8]]), 
#             loo(re_brms[[9]]), loo(re_brms[[10]]))

>>>>

```{r tn_fe, out.width="3.25in", out.height="4in"}
# lapply(re_brms, function(x) x$formula) 
fit_tn         <- re_brms[[9]] # 5 is best tn model with random effects
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

```{r re-comparison, fig.width=4}
# tp, tn
# ag, row_crop, pasture, corn, soybeans
re_global <- dplyr::rbind_all(lapply(re_brms, function(x) x$re_global))
re_global$term <- unlist(lapply(re_brms, 
                                function(x) get_re_text(as.character(x$formula)[1])))
re_global$response <- c(rep("tp", 5), rep("tn", 5))
re_global <- dplyr::filter(re_global, term != "rowvcropvpct")

### 2019-08-06 manuscript/appendix.Rmd
organize figs for ms

>>>>

```{r exploratory_heatmap, fig.cap = "Heatmap showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")
```

```{r hierarchical_demo, fig.cap = "A) Global (dashed line) and regional (solid lines) fits to the relationship between lake phosphorus and IWS Ag. land use cover from the 2011 NLCD. A hierarchical model would weight these relationships by sample size (darker lines = higher sample size). B) Number of lakes per region.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/02_hierarchical_demo-1.pdf")
```

```{r wetland_potential, fig.cap = "A) gSSURGO wetland potential versus National Wetlands Inventory cover. B) Locations of lakes where these number differ by more than 30 percent.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/03_wetland_potential-1.pdf")
```

```{r cafos, fig.cap = "Livestock data from the 2007 USDA Census of Agriculture.", warning=FALSE, echo = FALSE, eval=FALSE, eval=FALSE}
knitr::include_graphics("../figures/05_cafos-1.pdf")
```

```{r lulc_buffers, fig.cap = "Landuse cover in stream buffers.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/06_lulc_buffer_demo-1.pdf")
```

```{r cdl_viewport, fig.cap = "CDL landuse cover in example IWS.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/cdl_viewport-1.pdf")
```

```{r county_extent, fig.cap = "Number of lake watersheds per county where lakes are limited to those with high agricultural land-use cover (greater than 40 percent) and water quality data in LAGOS from at least 3 sampling events between 2000 and 2010.", warning=FALSE, echo = FALSE, eval = FALSE}
knitr::include_graphics("../figures/01_county_extent-1.pdf")
```

```{r maps, fig.cap = "Quantile map of lake nutrients.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/tptn_maps-1.pdf")
```

```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover. Line is 1:1 not regression.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
```

```{r nlcd-versus-cdl_map, fig.cap = "Comparison between NLCD (2011) ag and pasture against CDL (2010) specific crops.", warning=FALSE, echo = FALSE, eval = FALSE}
knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")
```

```{r lulc_vs_iws-lulc, fig.cap = "Stream buffer versus IWS lulc.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/09_stream_buffer-1.pdf")
```

```{r big_stream_ag, fig.cap = "Stream buffer Ag compared to IWS Ag.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/satellite-1.pdf")
```

### 2019-08-06 manuscript/figures.Rmd
organize figs for ms

```{r county_extent, fig.cap = "Number of lake watersheds per county where lakes are limited to those with high agricultural land-use cover (greater than 40 percent) and water quality data in LAGOS from at least 3 sampling events between 2000 and 2010.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/01_county_extent-1.pdf")
```

```{r maps, fig.cap = "Quantile map of lake nutrients.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/tptn_maps-1.pdf")
```

@@

```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover. Line is 1:1 not regression.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
```

```{r nlcd-versus-cdl_map, fig.cap = "Comparison between NLCD (2011) ag and pasture against CDL (2010) specific crops.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")
```

```{r lulc_vs_iws-lulc, fig.cap = "Stream buffer versus IWS lulc.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/09_stream_buffer-1.pdf")
```

```{r big_stream_ag, fig.cap = "Stream buffer Ag compared to IWS Ag.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/satellite-1.pdf")
```

@@

```{r exploratory_heatmap, fig.cap = "Heatmap showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")
```

```{r hierarchical_demo, fig.cap = "A) Global (dashed line) and regional (solid lines) fits to the relationship between lake phosphorus and IWS Ag. land use cover from the 2011 NLCD. A hierarchical model would weight these relationships by sample size (darker lines = higher sample size). B) Number of lakes per region.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/02_hierarchical_demo-1.pdf")
```

```{r wetland_potential, fig.cap = "A) gSSURGO wetland potential versus National Wetlands Inventory cover. B) Locations of lakes where these number differ by more than 30 percent.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/03_wetland_potential-1.pdf")
```

```{r cafos, fig.cap = "Livestock data from the 2007 USDA Census of Agriculture.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/05_cafos-1.pdf")
```

```{r lulc_buffers, fig.cap = "Landuse cover in stream buffers.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/06_lulc_buffer_demo-1.pdf")
```

```{r cdl_viewport, fig.cap = "CDL landuse cover in example IWS.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/cdl_viewport-1.pdf")
```

>>>>

\pagebreak

@@

@@

```{r fe-1, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/fe-1.pdf")
```

```{r re-comparison-1, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/re-comparison-1.pdf")
```

```{r re-1, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/re-1.pdf")
```

```{r tn_re_hu4-1, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/tn_re_hu4-1.pdf")
```

```{r tn_re_compare-1, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/tn_re_compare-1.pdf")
```
